---
title: "Inclass Assignment 2"
author: "Thu Nguyen"
date: "9/17/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

(a) Load the 'iris' and summarize it.

```{r}
data(iris)
summary(iris)

```

b) Use ggplot to create a scatterplot of Sepal.Length (x axis) with Petal.Length (y axis). 
Color the points by 'Species'. 
Label x axis as  'Sepal Length', y axis as 'Petal Length', and title as 'Iris Data'. 

```{r}
library(ggplot2)
```
```{r}
ggplot(iris, aes(x=Sepal.Length, y=Petal.Length, shape = Species, color = Species)) + 
   geom_point() + 
   ggtitle("Iris Data") + 
   theme(plot.title = element_text(hjust = 0.5))
```

(c) Use ggplot to create a side-by-side boxplot showing Sepal.Length for each species. 
Fill the boxplots with different colors by Species. 

```{r}
ggplot(iris, aes(x = Species, y=Sepal.Length, fill=Species)) + geom_boxplot() + theme(legend.position = "none")
```

I don't know if you are asking to make a similar plot like the previous question only with boxplot or something else. Here's another way 

```{r}
ggplot(iris, aes(x = Sepal.Length, y=Petal.Length, fill=Species))+geom_boxplot() + facet_wrap(~Species)

```
